Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-03 main.tex
reflection, ongoing

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
% \usepackage[margin=0.1cm]{geometry}
\input{header}

@@

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary simplex $S'$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        whenever $K \in \calS$ is an $n$-simplex, 
        we replace the vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
        giving us a simplex $K'$.

        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
        By construction, all these $n$-simplices contain $S$ as a subsimplex,
        and they are disjoint except for their proper subsimplices. 
        Hence $\calS'$ is indeed a triangulation. 
        Moreover, $S$ is an inner subsimplex of that triangulation. 
        In particular, $\calS'$ is its own star around $S$.

        \item 
        In what follows, we also use $\calR'$, 
        the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
        Then $\calR'$ is the local star around the barycenter $z_S$,
        and all $n$-simplices in $\calR'$ contain $z_{S}$. 
        We let $\calR$ and $\calR^{c}$ be the corresponding refinements of $\calS$ and $\calS^{c}$, respectively.

        The last simplicial complex that we introduce is called $\calK$,
        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.

@@

        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.

@@

        We then define 

@@

        By construction, the mapping preserves volumes:

@@

@@

        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,

@@

%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        By the definition of the tangent, $\tan(\beta) \leq \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$, and we know $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$. 
        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We write 
        \begin{align*}
            B_{T} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage[margin=0.1cm]{geometry}
\input{header}

@@

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        given any $n$-simplex $K \in \calS$, 
        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
        thus obtaining a new simplex $K'$. 
        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.

        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
        By construction, all its $n$-simplices contain $S$ as a subsimplex,
        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
        Moreover, $S$ is an inner subsimplex of that triangulation. 
        In particular, $\calS'$ is its own star around $S$.

        \mwl{Check that $\calS'$ is a triangulation...}

        \item 
        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
        Then $\calR'$ is its own local star around the barycenter $z_S$.
        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
        which we denote by $\calR$ and $\calR^{c}$, respectively.

        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.

@@

        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ between the underlying sets as follows.

@@

        Then the mapping 

@@

        preserves volumes:

@@

		Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 

@@

        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,

@@

%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        We develop explicit bounds for these singular values. 
        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.

        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in a face $F$ of $T$. 
        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of $F$ in $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We abbreviate 
        \begin{align*}
            B_{T} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}
